### 2017-12-14 submission/manuscript.Rmd
add bray-curtis diffs to manuscript

@@

***Statistical Analysis:***
All analysis was done with the R (v `r paste(version$major, ".", version$minor, sep = "")`) software package [@r_citation_2017]. Data tranformation and graphing was completed using the tidyverse package (v `r paste(packageVersion("tidyverse")[1])`) and colors selected using the viridis package (v `r paste(packageVersion("viridis")[1])`) [@tidyverse_2017; @viridis_citation_2017]. The total number of OTUs were analyzed using an ANOVA with a tukey post-hoc test. For the fecal samples the data was normalized to each individual by cycle number to account for the biological variation between different people. For both error and chimera analysis, samples were tested using Kruskal-Wallis with a Dunns post-hoc test. Where applicable correction for multiple comparison utilized the Benjamini-Hochberg method [@benjamini_controlling_1995].

***Analysis Workflow:***
The total number of OTUs after sub-sampling was analyzed for both the fecal and mock community samples. From these observations we wanted to next analyze potential reasons as to why some of these differences may have occured. First, analysis of general sequence error rate, number of sequences with an error, and base subsitution were assessed in the mock community for each Taq. After assessing these errors, the total number of chimeras was determined after sequence processing. The fecal samples were analyzed at 4 different sub-sampling levels, 1000, 5000, 10000, and 15000 while the mock community samples were analysed at 3 levels, 1000, 5000, 10000.

@@

>>>>

# Read in results from PERMANOVA and bray analysis
bray_sim_to_prev_cycle_kruskal_results <- as.data.frame(read_csv("../data/process/tables/bray_sim_to_prev_cycle_kruskal_results.csv"))
bray_permanova_by_taq_results <- as.data.frame(read_csv("../data/process/tables/bray_permanova_by_taq_results.csv"))

@@

***Statistical Analysis:***
All analysis was done with the R (v `r paste(version$major, ".", version$minor, sep = "")`) software package [@r_citation_2017]. Data tranformation and graphing was completed using the tidyverse package (v `r paste(packageVersion("tidyverse")[1])`) and colors selected using the viridis package (v `r paste(packageVersion("viridis")[1])`) [@tidyverse_2017; @viridis_citation_2017]. The total number of OTUs were analyzed using an ANOVA with a tukey post-hoc test. For the fecal samples the data was normalized to each individual by cycle number to account for the biological variation between different people. Bray-Curtis distance matrices were generated using mothur after 100 sub-samplings at 1000, 5000, 10000, and 15000. The distance matrix data was analyzed using PERMANOVA with the vegan package (v `r paste(packageVersion("vegan")[1])`) [@vegan_citation] and kruskal-wallis tests within R. For both error and chimera analysis, samples were tested using Kruskal-Wallis with a Dunns post-hoc test. Where applicable correction for multiple comparison utilized the Benjamini-Hochberg method [@benjamini_controlling_1995].

***Analysis Workflow:***
The total number of OTUs after sub-sampling was analyzed for both the fecal and mock community samples. Cycle dependent affects on Bray-Curits distances were next assessed for the fecal samples looking at both overall cycle differences and within individual differences for the previous cycle (e.g. 20 versus 25, 25 versus 30, etc.). From these observations we wanted to next analyze potential reasons as to why some of these differences may have occured. First, analysis of general sequence error rate, number of sequences with an error, and base subsitution were assessed in the mock community for each Taq. After assessing these errors, the total number of chimeras was determined after sequence processing. The fecal samples were analyzed at 4 different sub-sampling levels, 1000, 5000, 10000, and 15000 while the mock community samples were analysed at 3 levels, 1000, 5000, 10000.

@@

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
Using PERMANOVA to test whether there were any differences within HiFi DNA polymerase groups based on cycle number, only Phusion had cycle dependent differences at 1000 and 5000 sub-sampling depth (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)` and `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 5000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`, respectively). Interestingly, Phusion was one of only two DNA polymerase that managed to have samples for the 1000 sub-sampling depth at 15 cycles. Next, we assessed whether there were any major differences between 5 cycle increments within each sample. We found that there was no detectable difference in distance when comparing to the previous 5 cycle increment (P-value `r ifelse(min(bray_sim_to_prev_cycle_kruskal_results$bh, na.rm = T) > 0.05, invisible(">"), invisible("check data"))` 0.05). However, Phusion at 1000 sub-sampling depth had a P-value = `r format(filter(bray_sim_to_prev_cycle_kruskal_results, sub_sample_level == 1000, taq == "PHU")[, "pvalue"], digits = 1, nsmall = 1)` before multiple comparison correction. It should be noted that at higher sub-sampling depths these differences in Bray-Curits distance disappear for both differences in cycle number and within 5 cycle increments within an individual.

### 2017-12-14 submission/manuscript.tex
add bray-curtis diffs to manuscript

\textbf{\emph{Statistical Analysis:}} All analysis was done with the R
(v 3.4.2) software package (R Core Team, 2017). Data tranformation and
graphing was completed using the tidyverse package (v 1.1.1) and colors
selected using the viridis package (v 0.4.0) (Garnier, 2017; Wickham,
2017). The total number of OTUs were analyzed using an ANOVA with a
tukey post-hoc test. For the fecal samples the data was normalized to
each individual by cycle number to account for the biological variation
between different people. For both error and chimera analysis, samples
were tested using Kruskal-Wallis with a Dunns post-hoc test. Where
applicable correction for multiple comparison utilized the
Benjamini-Hochberg method (Benjamini \& Hochberg, 1995).

\textbf{\emph{Analysis Workflow:}} The total number of OTUs after
sub-sampling was analyzed for both the fecal and mock community samples.
From these observations we wanted to next analyze potential reasons as
to why some of these differences may have occured. First, analysis of
general sequence error rate, number of sequences with an error, and base
subsitution were assessed in the mock community for each Taq. After
assessing these errors, the total number of chimeras was determined
after sequence processing. The fecal samples were analyzed at 4
different sub-sampling levels, 1000, 5000, 10000, and 15000 while the
mock community samples were analysed at 3 levels, 1000, 5000, 10000.

@@

@@

>>>>

\textbf{\emph{Statistical Analysis:}} All analysis was done with the R
(v 3.4.2) software package (R Core Team, 2017). Data tranformation and
graphing was completed using the tidyverse package (v 1.1.1) and colors
selected using the viridis package (v 0.4.0) (Garnier, 2017; Wickham,
2017). The total number of OTUs were analyzed using an ANOVA with a
tukey post-hoc test. For the fecal samples the data was normalized to
each individual by cycle number to account for the biological variation
between different people. Bray-Curtis distance matrices were generated
using mothur after 100 sub-samplings at 1000, 5000, 10000, and 15000.
The distance matrix data was analyzed using PERMANOVA with the vegan
package (v 2.4.4) (Oksanen et al., 2017) and kruskal-wallis tests within
R. For both error and chimera analysis, samples were tested using
Kruskal-Wallis with a Dunns post-hoc test. Where applicable correction
for multiple comparison utilized the Benjamini-Hochberg method
(Benjamini \& Hochberg, 1995).

\textbf{\emph{Analysis Workflow:}} The total number of OTUs after
sub-sampling was analyzed for both the fecal and mock community samples.
Cycle dependent affects on Bray-Curits distances were next assessed for
the fecal samples looking at both overall cycle differences and within
individual differences for the previous cycle (e.g.~20 versus 25, 25
versus 30, etc.). From these observations we wanted to next analyze
potential reasons as to why some of these differences may have occured.
First, analysis of general sequence error rate, number of sequences with
an error, and base subsitution were assessed in the mock community for
each Taq. After assessing these errors, the total number of chimeras was
determined after sequence processing. The fecal samples were analyzed at
4 different sub-sampling levels, 1000, 5000, 10000, and 15000 while the
mock community samples were analysed at 3 levels, 1000, 5000, 10000.

@@

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} Using PERMANOVA to test whether there were any differences
within HiFi DNA polymerase groups based on cycle number, only Phusion
had cycle dependent differences at 1000 and 5000 sub-sampling depth
(P-value = 0.03 and 0.01, respectively). Interestingly, Phusion was one
of only two DNA polymerase that managed to have samples for the 1000
sub-sampling depth at 15 cycles. Next, we assessed whether there were
any major differences between 5 cycle increments within each sample. We
found that there was no detectable difference in distance when comparing
to the previous 5 cycle increment (P-value \textgreater{} 0.05).
However, Phusion at 1000 sub-sampling depth had a P-value = 0.02 before
multiple comparison correction. It should be noted that at higher
sub-sampling depths these differences in Bray-Curits distance disappear
for both differences in cycle number and within 5 cycle increments
within an individual.

@@

\hypertarget{ref-vegan_citation}{}
Oksanen J., Blanchet FG., Friendly M., Kindt R., Legendre P., McGlinn
D., Minchin PR., O'Hara RB., Simpson GL., Solymos P., Stevens MHH.,
Szoecs E., Wagner H. 2017. \emph{Vegan: Community ecology package}.
